Tilting at Algorithmic Windmills

### 2013-05-14 Tilting/Rpaper.Rnw
WIP: small comments on why co-authors should run your code

\section{Introduction}
The neuroscience community has significantly benefited from the proliferation
of imaging software.  Established packages such as SPM \cite{Ashburner2012},
the FMRIB Software Library (FSL) \cite{Jenkinson2012}, and
the AFNI toolkit \cite{cox2012} have aided neuroimaging researchers 
around the world in performing complex analyses as part of 
ongoing neuroscience research.  Parallel to this line of
inquiry is continued algorithmic innovation for improvement
in analysis tools.

@@

Although different journals have varying guidelines for determining 
co-authorship, there is at least an implied sense of responsibility for
an article's contents assumed by each of the co-authors.  Strategies 
taken by journal editorial boards are being used to reduce undeserving
authorship attribution such as requiring the listing of the specific 
contributions of each co-author.  Additional proposals have included
signed statements of responsibility for the contents of the article 
\cite{nature2007}.  We suggest that at least one co-author
independently verify a subset of the results by running the processing
on their own computer.

@@

\subsubsection{Provide computational platform details of the evaluation}
An recent article \cite{gronenschild2012} pointed out significant
differences in Freesurfer output that varied with Freesurfer release
version and with operating systems.  While the former is to be
expected given upgrades and big fixes which occur between releases,
the latter underscores both the need for consistency in study processing
as well as the reporting of computational details for reproducibility.

>>>>

\section{Introduction}
The neuroscience community has significantly benefitted from the proliferation
of imaging software.  Established packages such as SPM \cite{Ashburner2012},
the FMRIB Software Library (FSL) \cite{Jenkinson2012}, and
the AFNI toolkit \cite{cox2012} have aided neuroimaging researchers 
around the world in performing complex analyses as part of 
ongoing neuroscience research.  Parallel to this line of
inquiry is continued algorithmic innovation for improvement
in analysis tools.

@@

Although different journals have varying guidelines for determining 
co-authorship, there is at least an implied sense of responsibility for
an article's contents assumed by each of the co-authors.  Strategies 
taken by journal editorial boards are being used to reduce undeserving
authorship attribution such as requiring the listing of the specific 
contributions of each co-author.  Additional proposals have included
signed statements of responsibility for the contents of the article 
\cite{nature2007}.  We suggest that at least one co-author
independently verify a subset of the results by running the processing
on their own computer.   The point of this excercise is to verify not only
reproducibility but also that the process can be explained in
sufficient detail.

@@

\subsubsection{Provide computational platform details of the evaluation}
An recent article \cite{gronenschild2012} pointed out significant
differences in Freesurfer output that varied with Freesurfer release
version and with operating systems.  While the former is to be
expected given upgrades and bug fixes which occur between releases,
the latter underscores both the need for consistency in study processing
as well as the reporting of computational details for reproducibility.
